
% translated by spod2latex from hemat.pod on Fri Sep 29 13:48:47 EDT 2006
\subsection{The \macro{HEMAT}: HE plots for all pairs of response variables}\label{mac:hemat}
 \index{\macro{hemat}}

The \macro{HEMAT} plots the covariance ellipses for a hypothesized (H)
effect and for error (E) for all pairs of variables from a MANOVA
or multivariate multiple regression.

\subsubsection*{Method}

The macro calls HEPLOT within nested \%do ... \%end loops to plot all
pairs of responses.  This is wrapped with calls to the \macro{GDISPLA} 
to suppress display of the individual plots.  The final display is
produced by \PROC{GREPLAY}.  In order to make this macro reusable with
a single SAS session, the separate plots are saved in a temporary
graphics catalog (\texttt{GTEMP=work.gtemp}), which is normally deleted at the end
(\texttt{GKILL=Y}).

\subsubsection*{Usage}

The \macro{HEMAT} is defined with keyword parameters.
The arguments may be listed within parentheses in any order, separated
by commas. For example:

\begin{listing}
 %hemat(data=iris, stat=stats, 
    var=SepalLen SepalWid PetalLen PetalWid,
    effect=species);
\end{listing}
\subsubsection*{Parameters}
\begin{proglist}

\item[DATA=] Name of the raw data set to be plotted. \default{DATA=_LAST_}

\item[STAT=] Name of \texttt{OUTSTAT=} dataset from \PROC{GLM}

\item[EFFECT=] Name of MODEL effect to be displayed for the H matrix.
This must be one of
the terms on the right hand side of the MODEL statement used
in the \PROC{GLM} or \PROC{REG} step, in the same format that this
efffect is labeled in the \texttt{STAT=} dataset. This must be one of
the values of the \verb|_SOURCE_| variable contained in the \texttt{STAT=} 
dataset.

\item[VAR=] Names of response variables to be plotted - can be
a list or \texttt{X1-X4} or \texttt{VARA--VARB}. \default{VAR=_NUMERIC_}

\item[NAMES=] Alternative variable names (used to label the diagonal
cells.)

\item[M1=] First matrix: either H or H+E. \default{M1=H}

\item[M2=] Second matrix either E or I. \default{M2=E}

\item[SCALE=] Scale factors for M1 and M2.  See description in HEPLOT

\item[HTITLE=] Height of variable name in diagonal cells

\item[SYMBOLS=] Not used

\item[COLORS=] Colors for the H and E ellipses. \default{COLORS=BLACK RED}

\item[ANNO=] Annotate diag or off-diag plot. \default{ANNO=NONE}

\item[GTEMP=] Temporary graphics catalog. \default{GTEMP=GTEMP}

\item[KILL=] Delete grtemp when done. \default{KILL=Y}

\item[GOUT=] Name of the graphic catalog. \default{GOUT=GSEG}

\end{proglist}
